### 2014-02-28 paper/retrofit.tex
rm formal from retrofit.tex
Minor formatting updates.
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

\begin{figure}
\begin{code}
tv   ::= \tx.te | true | false | ta
tty   ::= bool | tty -> tty | ref tty
te   ::= tv | tx | te te | if te then te else te | ref te | !te | te := te
tE   ::= tHole | tE te | tv tE | if tE then te else te
       | ref tE | !tE | tE := te | tv := tE

@@

\Red{Suggestion: Only give the rules for references, because otherwise this is all standard.}

@@

\and
\inferrule[T-ref]
{| tS' = tS [ ta mapsto tv ] | } 
{| conf tS (ref tv) -> conf tS' ta |}
{| fresh (ta) |}

\and
\inferrule[T-deref]
{| tv = tS(ta) |}
{| conf tS (!ta) -> conf tS tv |}

\and
\inferrule[T-ass]
{| tS' = tS [ ta mapsto tv ] |} 
{| conf tS (ta := tv) -> conf tS' tv |}
\end{mathpar}

>>>>

\begin{figure}
\begin{code}
tv   ::= \tx.te | true | false | ta
te   ::= tv | tx | te te | if te then te else te | ref te | !te | te := te
tE   ::= tHole | tE te | tv tE | if tE then te else te
       | ref tE | !tE | tE := te | tv := tE

@@

@@

\and
\inferrule[T-ref]
{ }
{| conf tS (ref tv) -> conf (tS [ ta mapsto tv ]) ta |}
{| fresh ta |}

\and
\inferrule[T-deref]
{ }
{| conf tS (!ta) -> conf tS (ap ts ta) |}

\and
\inferrule[T-ass]
{ }
{| conf tS (ta := tv) -> conf (tS [ ta mapsto tv ]) tv |}
\end{mathpar}
